Supplementary Figures relative to dimensionality reduction

### 2020-02-28 supplementary_figures/supp5_dr.Rmd
added figure on k in maxLikGlobal

>>>>

```{r, include=FALSE, eval=FALSE}
source(system.file("extdata", "scrna_alternatives.R", package="pipeComp"))
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(Seurat)
  library(scater)
  library(intrinsicDimension)
})
datasets <- list.files("../datasets", full.names = TRUE)
names(datasets) <- gsub("\\..*", "", basename(datasets))
datasets <- lapply(datasets, readRDS)
datasets <- lapply(datasets, filt.mad)
datasets <- lapply(datasets, norm.seurat)
datasets <- lapply(datasets, sel.deviance)

met <- c("seurat.pca", "scran.denoisePCA", "scran.runPCA")
res <- list()
for(i in met) {
  res[[i]] <- list()
  print(i)
  a <- lapply(datasets, function(x) {
    switch(i,
           seurat.pca = seurat.pca(x),
           scran.denoisePCA = scran.denoisePCA(x),
           scran.runPCA = scran.runPCA(x))
  })
  x <- lapply(a, function(x) reducedDim(x, "PCA"))
  rm(a); gc()
  ks <- seq(5, 40, 5)
  for (d in names(datasets)) {
    res[[i]][[d]]$ndims <- c()
    res[[i]][[d]]$k <- c()
  }
  for (k in ks) {
    print(paste("k:", k))
    for (d in names(datasets)) {
      res[[i]][[d]]$ndims <- c(res[[i]][[d]]$ndims,
                               as.numeric(maxLikGlobalDimEst(x[[d]], k=k, unbiased=TRUE)))
      res[[i]][[d]]$k <- c(res[[i]][[d]]$k, k)
    }
  }
}
saveRDS(res, "../data/maxLikGlobal.rds")
```

```{r, fig.width=7, fig.height=5}
res <- readRDS("../data/maxLikGlobal.rds")
res <- dplyr::bind_rows(lapply(res$seurat.pca, as.data.frame), .id="dataset")
cols <- pipeComp::getQualitativePalette(9)
names(cols) <- unique(res$dataset)
ggplot(res, aes(k, ndims, colour=dataset)) + geom_point() + geom_line() + 
  scale_colour_manual(values=cols) + xlab("Number of nearest neighbors (k)") +
  ylab("Estimated dimensionality") + 
  ggtitle("intrinsicDimension::maxLikGlobalDimEst")
```

### Supplementary Figure `r getFigNb()`
Estimates of dimensionality by the `intrinsicDimension::maxLikGlobalDimEst` method using various 'reasonable' numbers of nearest neighbors (`k` parameter).
